Implementing Real-time Transport Services over an Ossified Network

### 2016-05-18 paper.tex
Drafts 'Partial Reliability and TCP' section

The implication of this reality is that it is difficult to deploy new 
transport protocols. The installed base of NATs, firewalls, and other
middleboxes is such that packets that do not look like TCP or UDP are
unlikely to pass the network. We may innovate all we like, provided the
transport of the future looks like TCP or UDP to middleboxes.\footnote{
  This is inconvenient, certainly, but is not necessarily a bad thing. 
  The Internet is critical infrastructure. It support emergency services, 
  healthcare applications, infrastructure components, financial services, 
  and so on, many of which are essential to the functioning of society. 
  Making changes to this type of infrastructure \emph{should} require 
  careful backwards compatibility.
}

@@

approach: 
- separate out sequence numbers in sent segments with sequence numbers
  visible to the application.
- COBS encode for message boundaries.
- retransmission have same segment sequence number, but different contents
  and application sequence numbers

Does it work?
- Initial deployment results from the UK
- Is there any more data that can be got quickly?

Any other surveys showing the same thing?

>>>>

The implication of this reality is that it is difficult to deploy new 
transport protocols. The installed base of NATs, firewalls, and other
middleboxes is such that packets that do not look like TCP or UDP are
unlikely to pass the network. We may innovate all we like, provided the
transport of the future looks like TCP or UDP to middleboxes.\footnote{
  This is inconvenient, certainly, but is not necessarily a bad thing. 
  The Internet is critical infrastructure. It support emergency services, 
  healthcare applications, infrastructure components, financial services, 
  and so on, many of which are essential to the functioning of society. 
  Making changes to this type of infrastructure \emph{should} require 
  careful backwards compatibility \cite{mcquistin:2015:reinterpreting}.
}

@@

Partial reliability (i.e., reliability conditional on timing and dependency
information) can be implemented by relaxing TCP's reliability guarantee.
The implication of this is that we need to offer a message-oriented
abstraction to applications. If the arrival of a segment cannot be
guaranteed, then it is not possible to offer a byte stream abstraction.

To offer a message-oriented abstraction, the boundaries between each
message must be maintained between sender and receiver. This means that a
framing mechanism is required: it is not sufficient to send each message in
a single segment, as this mapping will not necessarily be maintained by the
network. A framing marker is added to the start and end of each message
before transmission. An encoding algorithm is used to escape all occurences
of the framing marker within the message data. This process does not impact
on the data that can be sent or received by applications.

In order to maintain compatibility with middleboxes, offering partial
reliability requires using \emph{inconsistent retransmissions}. This means
that the mapping between message data and TCP sequence numbers is no longer
static: a given TCP sequence number may be relate to different messages at
different times. Therefore, an application-level sequence number is
required to allow messages to be uniquely identified.

When a TCP segment is to be retransmitted, the current mapping between its
sequence number and application-level sequence numbers is used to determine
which messages within the segment are to be retransmitted. A liveness check
is performed on these messages, to determine that (i) the message will
arrive on time to be played out; and (ii) the message does not depend on an
expired message. For (i), we combine the time that the message has spent in
a sending queue, with an estimate of the round-trip time and the current
play-out delay. This is then compared against the lifetime of the message,
as expressed by the application. For (ii), we maintain metadata about
sequence numbers that have expired, and check this metadata for the
dependency expressed by the application.

This mechanism -- inconsistent retransmissions -- is visible to middleboxes
on the network that are performing payload inspection. These middleboxes
may interpret this behaviour relating to an attack. For example, a
man-on-the-side attack exhibits similar behaviour, where a malicious host
is injecting data into an existing TCP flow. As a result, our connection
may be disrupted. Honda et al. \cite{honda:2011:extend-tcp} conducted
experiments across 135 paths on the Internet, to determine support for
inconsistent retransmissions. The observed that the majority of paths
delivered inconsistent retransmissions successfully. On Port 80 (HTTP), the
original segment was delivered on 7\% of paths tested. Only one connection
reset was observed. We conducted further deployability experiments using
inconsistent retransmissions \cite{mcquistin2016hollywood}, and found that
fixed-line networks delivered inconsistent retransmissions successfully,
but that delivery of the original segment was common on cellular networks.

These deployability experiments suggest that our protocol should be
flexible: inconsistent retransmissions may not be delivered, and we should
handle reception of the original segment. If the protocol detects that
inconsistent retransmissions are not being delivered, then the mechanism
can be disabled for the connection. Further, if a connection reset occurs,
then the connection should be retried with the mechanism disabled.

\todo{Add discussion on checksumming to maintain message integrity}
